Comparative Analysis of Discount Rates Across Grocery Vendors

### 2024-11-21 paper/paper.qmd
fix cross-reference

In @fig-daily, which depicts Simpson's Paradox, missing data points could further exacerbate discrepancies between aggregate and vendor-specific trends. If discount records for certain vendors were inconsistent, this could make it difficult to discern actual trends. Handling missing data carefully is essential to avoid biases in our interpretation. In this analysis, any such gaps would affect our ability to capture accurate month-to-month fluctuations or correctly interpret vendor-specific trends. Future studies should strive to include complete datasets or apply robust imputation techniques to fill any missing values, ensuring that the analysis reflects a fuller picture of discount patterns.

@@

Finally, Simpson's Paradox, as illustrated in @fig-daily, indicates an aggregation bias in our analysis. While the aggregate trend might suggest an overall stability or gradual increase in discount rates, individual vendors display unique trends that differ from the aggregate. This phenomenon emphasizes the need to disaggregate data to understand vendor-specific behaviors accurately, as aggregation can obscure meaningful individual patterns.

>>>>

In @fig-paradox, which depicts Simpson's Paradox, missing data points could further exacerbate discrepancies between aggregate and vendor-specific trends. If discount records for certain vendors were inconsistent, this could make it difficult to discern actual trends. Handling missing data carefully is essential to avoid biases in our interpretation. In this analysis, any such gaps would affect our ability to capture accurate month-to-month fluctuations or correctly interpret vendor-specific trends. Future studies should strive to include complete datasets or apply robust imputation techniques to fill any missing values, ensuring that the analysis reflects a fuller picture of discount patterns.

@@

Finally, Simpson's Paradox, as illustrated in @fig-paradox, indicates an aggregation bias in our analysis. While the aggregate trend might suggest an overall stability or gradual increase in discount rates, individual vendors display unique trends that differ from the aggregate. This phenomenon emphasizes the need to disaggregate data to understand vendor-specific behaviors accurately, as aggregation can obscure meaningful individual patterns.
